### 2019-12-12 paper/paper.tex
added paper stub

\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{floatflt}
\usepackage{blindtext}
\usepackage{enumitem}
\usepackage{amsthm}
\usepackage{subfig}
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{amsmath}
\usepackage{framed}
\usepackage{titling}
\usepackage{minibox}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage[strict]{changepage}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{matrix}
\pgfplotsset{width=11cm,compat=1.9}
\usepgfplotslibrary{external}
\tikzexternalize

\definecolor{vgreen}{RGB}{104,180,104}
\definecolor{vblue}{RGB}{49,49,255}
\definecolor{vorange}{RGB}{255,143,102}
\lstdefinestyle{bash} {language=bash, basicstyle=\ttfamily,
	keywordstyle=\color{vblue}, identifierstyle=\color{black},
	commentstyle=\color{vgreen}, tabsize=4,
%	moredelim=*[s][\colorIndex]{[}{]},
	literate=*{:}{:}1}

\lstdefinestyle{caml} {language=caml, basicstyle=\ttfamily, columns=[c]fixed,
 keywordstyle=\color{vblue}, identifierstyle=\color{black},
 commentstyle=\color{vgreen}, upquote=true, commentstyle=, breaklines=true,
 showstringspaces=false, stringstyle=\color{blue},
 literate={'"'}{\textquotesingle "\textquotesingle}3}

\title{Minicaml, a purely functional, didactical programming language with an
interactive REPL.}
\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari and Prof. Francesca Levi}
\begin{document}
\begin{titlingpage}
\maketitle

\begin{abstract}
\textbf{minicaml} is a small, purely functional interpreted programming language
with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and
Prof. Francesca Levi's minicaml, an evaluation example to show students
attending the Programming 2 course at the University of Pisa how interpreters
work. It is an interpreted language with a Caml-like syntax, featuring
interchangeable eager and lazy evaluation, a didactical REPL
that shows each AST expression and each evaluation step.
\end{abstract}
\end{titlingpage}

Test
\end{document}

### 2019-12-23 paper/paper.tex
working on the paper

@@
 \usepackage{minibox}
+\usepackage{hyperref}
 \usepackage{float}
@@
 interactive REPL.}
-\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari and Prof. Francesca Levi}
+\author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
 \begin{document}
@@
 \textbf{minicaml} is a small, purely functional interpreted programming language
-with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and
-Prof. Francesca Levi's minicaml, an evaluation example to show students
-attending the Programming 2 course at the University of Pisa how interpreters
-work. It is an interpreted language with a Caml-like syntax, featuring
-interchangeable eager and lazy evaluation, a didactical REPL
-that shows each AST expression and each evaluation step.
+with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and Prof.
+Francesca Levi's minicaml, an evaluation example to show students attending the
+Programming 2 course at the University of Pisa how interpreters work. It is an
+interpreted language with a Caml-like syntax, featuring interchangeable eager
+and lazy evaluation and a didactical REPL that shows each AST expression and
+each evaluation step.
 \end{abstract}
@@
 
-Test
+\section{REPL and command line interface}
+\subsection{Installation}
+\textbf{minicaml} is available in the opam 2.0 repository.
+(\url{https://opam.ocaml.org/}). The easiest way to install minicaml is with the
+OCaml package manager \textbf{opam}. To do so, please check that you have a version of opam $\geq$
+2.0.0 and run:
+\begin{lstlisting}[style=bash]
+opam install minicaml
+\end{lstlisting}
+Alternatively, \textbf{minicaml} can be installed from source by downloading the
+source code git repository and building it manually. \textbf{minicaml} has been tested
+only on Linux and macOS systems. It has not been tested yet on Windows and BSD
+derived systems.
+\begin{lstlisting}[style=bash]
+# download the source code
+git clone https://github.com/0x0f0f0f/minicaml
+# cd into the source code directory
+cd minicaml
+# install dependencies
+opam install ANSITerminal dune ppx_deriving menhir cmdliner
+# compile
+make
+# execute
+make run
+# install
+make install
+\end{lstlisting}
+
+\section{Lexer}
+
+\section{Parser}
+
+\section{AST Optimization}
+
+\section{Evaluation}
+
+\section{Tests}
+
+\section{Thanks}
+Thanks to Antonio DeLucreziis for helping me introduce lazy evaluation.
+
 \end{document}

### 2019-12-23 paper/paper.tex
optimizer optimizations >:)

@@
 \section{AST Optimization}
+Before being evaluated, AST expressions are analyzed and optimized by an
+optimizer function that is recursively called over the tree that is representing
+the expression. To achieve minimization to an unreducible (not optimizable)
+form, optimizer calls are iterated on each previous call's result; this way,
+when a tree representing an expression cannot be optimized again.
+This is the process represented in pseudo-code:
 
@@
 \section{Tests}
+Unit testing is extensively performed using the alcotest testing framework.
 

### 2019-12-23 paper/paper.tex
paper

@@
 optimizer function that is recursively called over the tree that is representing
-the expression. To achieve minimization to an unreducible (not optimizable)
-form, optimizer calls are iterated on each previous call's result; this way,
-when a tree representing an expression cannot be optimized again.
-This is the process represented in pseudo-code:
+the expression. The optimizer simplifies expressions which result is known and
+therefore does not need to be evaluated. For example, it is known that \texttt{5
++ 3 $\equiv$ 8} and \texttt{true \&\& (true || (false \&\& false)) $\equiv$
+true}. When a programmer writes a program, she or he may not want to do all the
+simple calculations before writing the program in which they appear in, we rely
+on machines to simplify those processes. Reducing constants before evalaution
+may seem unnecessary when writing a small program, but they do take away
+computation time, and if they appear inside of loops, it is a wise choice to
+simplify those constant expressions whose result is already known before it is
+calculated in all the loop iterations. To achieve minimization to an unreducible form, optimizer calls are iterated on
+each previous call's result; this way, we get a tree representing an expression
+that cannot be optimized again. This process is fairly easy:
+
+\begin{lstlisting}[style=caml]
+let rec iterate_optimizer e =
+	let oe = optimize e in
+	if oe = e then e (* Bottoms out *)
+	else iterate_optimizer oe
+\end{lstlisting}
 
@@
 \section{Thanks}
-Thanks to Antonio DeLucreziis for helping me introduce lazy evaluation.
+Thanks to Antonio DeLucreziis for helping me implement lazy evaluation.
 

### 2019-12-23 paper/paper.tex
added list and dictionary map function

@@
 simplify those constant expressions whose result is already known before it is
-calculated in all the loop iterations. To achieve minimization to an unreducible form, optimizer calls are iterated on
-each previous call's result; this way, we get a tree representing an expression
-that cannot be optimized again. This process is fairly easy:
+calculated in all the loop iterations. It is also necessary in optimizing
+programs before compilation. The optimizer, by now, reduces operations between
+constants and \texttt{if} statements whose guard is always true (or false). To
+achieve minimization to an unreducible form, optimizer calls are repeated until
+it produces an output equal to its input; this way, we get a tree representing
+an expression that cannot be optimized again. This process is fairly easy:
 
@@
 \end{lstlisting}
+
+\section{Types}
 

### 2019-12-25 paper/paper.tex
added more primitives, added bisect_ppx for test coverage, added more test cases

@@
 Programming 2 course at the University of Pisa how interpreters work. It is an
-interpreted language with a Caml-like syntax, featuring interchangeable eager
-and lazy evaluation and a didactical REPL that shows each AST expression and
-each evaluation step.
+interpreted language featuring a Caml-like syntax, static (lexical scoping),
+interchangeable eager and lazy evaluation and a didactical REPL that
+shows each AST expression and each evaluation step.
 \end{abstract}

### 2019-12-25 paper/paper.tex
working on paper

@@
 \title{Minicaml, a purely functional, didactical programming language with an
-interactive REPL.}
+interactive REPL. WORK IN PROGRESS DRAFT}
 \author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
@@
 \section{Tests}
-Unit testing is extensively performed using the alcotest testing framework.
+Unit testing is extensively performed using the alcotest testing framework. Code
+coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
+page when tests are run by dune.
 

### 2019-12-25 paper/paper.tex
opam version bump and paper progress

@@
 coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
-page when tests are run by dune.
+page containing the coverage percentage when unit tests are run by the dune
+build system. After each commit is pushed to the remote source repository on
+Github, the package is built and tests are run by the Travis Continuos
+Integration system.
 

### 2019-12-25 paper/paper.tex
fixed wrong opam file

@@
-\documentclass[12pt]{article}
+\documentclass[a4paper, 11pt]{article}
 
+%% Language and font encodings. This says how to do hyphenation on end of lines.
+\usepackage[english]{babel}
 \usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{floatflt}
-\usepackage{blindtext}
-\usepackage{enumitem}
-\usepackage{amsthm}
-\usepackage{subfig}
+\usepackage[T1]{fontenc}
 \usepackage{listings}
 \usepackage{listingsutf8}
-\usepackage{amsmath}
-\usepackage{framed}
-\usepackage{titling}
-\usepackage{minibox}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{longtable}
-\usepackage[strict]{changepage}
-\usepackage{pgfplots}
-\usepackage{tikz}
-\usetikzlibrary{matrix}
-\pgfplotsset{width=11cm,compat=1.9}
-\usepgfplotslibrary{external}
-\tikzexternalize
+\usepackage{xcolor}
+\usepackage{multicol}
+\setlength{\columnsep}{1cm}
+\setlength{\columnseprule}{0.5pt}
+%\usepackage{aas_macros}
+
+%% Sets page size and margins. You can edit this to your liking
+\usepackage[top=1.3cm, bottom=2.0cm, outer=2.5cm, inner=2.5cm, heightrounded,
+marginparwidth=1cm, marginparsep=0.4cm, margin=1.5cm]{geometry}
+
+%% Useful packages
+\usepackage{graphicx} %allows you to use jpg or png images. PDF is still recommended
+\usepackage[colorlinks=False]{hyperref} % add links inside PDF files
+\usepackage{amsmath}  % Math fonts
+\usepackage{amsfonts} %
+\usepackage{amssymb}  %
 
@@
 
+%% Citation package
+\usepackage[authoryear]{natbib}
+\bibliographystyle{abbrvnat}
+\setcitestyle{authoryear,open={(},close={)}}
+
 \title{Minicaml, a purely functional, didactical programming language with an
@@
 \author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
+
 \begin{document}
-\begin{titlingpage}
 \maketitle
@@
 \end{abstract}
-\end{titlingpage}
 
@@
 
+\begin{multicols}{2}
 \section{Lexer}
@@
 page containing the coverage percentage when unit tests are run by the dune
-build system. After each commit is pushed to the remote source repository on
-Github, the package is built and tests are run by the Travis Continuos
+build system. After each commit is pushed to the remote version control repository on
+Github, the package is built and tests are run thanks to the Travis Continuos
 Integration system.
 
-\section{Thanks}
-Thanks to Antonio DeLucreziis for helping me implement lazy evaluation.
+\section{Thanks to}
 
+\begin{itemize}
+	\item Prof. Gian-Luigi Ferrari for teaching us how to project and develop
+	interpreters in OCaml
+	\item Antonio DeLucreziis for helping me implement lazy evaluation.
+	\item Prof. Alessandro Berarducci for helping me study lambda calculus in deep.
+\end{itemize}
+
+\end{multicols}
 \end{document}

### 2019-12-25 paper/paper.tex
0.3 release

@@
 \usepackage{listings}
-\usepackage{listingsutf8}
 \usepackage{xcolor}
+%\usepackage{tgpagella} % text only
+\usepackage{mathpazo}
 \usepackage{multicol}
-\setlength{\columnsep}{1cm}
+\setlength{\columnsep}{1.5cm}
 \setlength{\columnseprule}{0.5pt}
@@
 \usepackage[top=1.3cm, bottom=2.0cm, outer=2.5cm, inner=2.5cm, heightrounded,
-marginparwidth=1cm, marginparsep=0.4cm, margin=1.5cm]{geometry}
+marginparwidth=1cm, marginparsep=0.4cm, margin=1.2cm]{geometry}
 
@@
 
-\title{Minicaml, a purely functional, didactical programming language with an
-interactive REPL. WORK IN PROGRESS DRAFT}
+\title{Minicaml, a purely functional, didactical programming language\\WORK IN PROGRESS DRAFT}
 \author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
@@
 # install dependencies
-opam install ANSITerminal dune ppx_deriving menhir cmdliner
+opam install ANSITerminal dune ppx_deriving menhir \\
+  cmdliner alcotest bisect_ppx
 # compile
 make
+# test
+make test
 # execute
@@
 
+\clearpage
+
 \begin{multicols}{2}
+
 \section{Lexer}
+
+Lexing is achieved with \texttt{ocamllex}, the default tool for generating
+scanners in OCaml
 

### 2020-01-07 paper/paper.tex
makefile
paper and opam spec
operational semantics in paper

@@
 \setcitestyle{authoryear,open={(},close={)}}
+
+\newcommand{\te}[1]{\text{#1}}
 
@@
 
+Boolean operations are reduced using laws from the propositional calculus, such as DeMorgan's law, complement, absorption and other trivial ones.
+
 \section{Types}
@@
 \section{Evaluation}
+\subsection{Operational Semantics}
+
+\textbf{Dictionaries}\\
+Note that the evaluation step of the dictionary is considered implicit.
+
+\begin{gather*}
+	\te{Insertion} \\
+	\hline \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow
+	\te{true}}{<\te{env, insert k v dict}> \Rightarrow \te{dict} \cup (\te{k,v})} \\ \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, insert k v dict}> \Rightarrow \te{dict}} \\ \\
+	\te{Deletion} \\ \hline \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, remove k dict}> \Rightarrow \te{dict} \textbackslash \{(\te{k,v})\}} \\ \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, remove k dict}> \Rightarrow \te{error}} \\ \\
+	\te{Contains key} \\ \hline \\
+	<\te{env}, \te{haskey k dict}> \Rightarrow \te{k} \in \te{dict} \\ \\
+	\te{Retreive a value} \\ \hline \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, getkey k dict}> \Rightarrow \te{v}} \\ \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, getkey k dict}> \Rightarrow \te{error}} \\ \\
+	\te{Filter by keys} \\ \hline \\
+	\dfrac{<\te{env, ks}> \Rightarrow \te{\{k1, ..., kn\}}}{<\te{env, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{d} \mid (k \in ks) \}} \\ \\
+	\te{Map} \\ \hline \\
+	\dfrac{<\te{env, f}> \Rightarrow \lambda(x)}{<\te{env, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{d}  \}} \\ \\
+	\te{Fold Left} \\ \hline \\
+	\dfrac{\begin{aligned}
+		<\te{env, f}> \Rightarrow \lambda(x,y)  \\
+		<\te{env, d}> \Rightarrow \{(k_1, v_1), \hdots, (k_n, v_n)\}
+	\end{aligned}}{<\te{env, foldl f a d}> \Rightarrow \lambda( \hdots \lambda(\lambda(a, v_1), v_2), \hdots, v_n)} \\ \\
+\end{gather*}
 

### 2020-01-07 paper/paper.tex
paper

@@
 \usepackage{xcolor}
+\usepackage{collectbox}
 %\usepackage{tgpagella} % text only
 \usepackage{mathpazo}
+
 \usepackage{multicol}
@@
 \newcommand{\te}[1]{\text{#1}}
+\newcommand{\mybox}{%
+    \collectbox{%
+        \setlength{\fboxsep}{1pt}%
+        \fbox{\BOXCONTENT}%
+    }%
+}
 
@@
 \textbf{Dictionaries}\\
-Note that the evaluation step of the dictionary is considered implicit.
+Note that the evaluation step of the dictionary is considered implicit in most
+cases. Primitives require that the arguments passed are already evaluated,
+therefore dictionaries are considered already evaluated. An exception is made
+for the \textit{Fold Left} catamorphism, where the key-value couples have
+to be enumerated in order to show the set-theoretic representation of a left fold.
 
@@
 	\te{true}}{<\te{env, insert k v dict}> \Rightarrow \te{dict} \cup (\te{k,v})} \\ \\
-	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, insert k v dict}> \Rightarrow \te{dict}} \\ \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, insert k v dict}> \Rightarrow \te{dict}}
+\end{gather*}
+\begin{gather*}
 	\te{Deletion} \\ \hline \\
 	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, remove k dict}> \Rightarrow \te{dict} \textbackslash \{(\te{k,v})\}} \\ \\
-	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, remove k dict}> \Rightarrow \te{error}} \\ \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, remove k dict}> \Rightarrow \te{error}}
+\end{gather*}
+\begin{gather*}
 	\te{Contains key} \\ \hline \\
-	<\te{env}, \te{haskey k dict}> \Rightarrow \te{k} \in \te{dict} \\ \\
+	<\te{env}, \te{haskey k dict}> \Rightarrow \te{k} \in \te{dict}
+\end{gather*}
+\begin{gather*}
 	\te{Retreive a value} \\ \hline \\
 	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, getkey k dict}> \Rightarrow \te{v}} \\ \\
-	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, getkey k dict}> \Rightarrow \te{error}} \\ \\
+	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, getkey k dict}> \Rightarrow \te{error}}
+\end{gather*}
+\begin{gather*}
 	\te{Filter by keys} \\ \hline \\
-	\dfrac{<\te{env, ks}> \Rightarrow \te{\{k1, ..., kn\}}}{<\te{env, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{d} \mid (k \in ks) \}} \\ \\
+	\dfrac{<\te{env, ks}> \Rightarrow \te{\{k1, ..., kn\}}}{<\te{env, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{d} \mid (k \in ks) \}}
+\end{gather*}
+\begin{gather*}
 	\te{Map} \\ \hline \\
-	\dfrac{<\te{env, f}> \Rightarrow \lambda(x)}{<\te{env, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{d}  \}} \\ \\
+	\dfrac{<\te{env, f}> \Rightarrow \lambda(x)}{<\te{env, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{d}  \}}
+\end{gather*}
+\begin{gather*}
 	\te{Fold Left} \\ \hline \\

### 2020-01-07 paper/paper.tex
operational semantics corrections

--- 2019-12-25 paper/paper.tex
@@
 \usepackage{xcolor}
+\usepackage{mathtools}
+\usepackage{amsthm}
+\usepackage{collectbox}
 %\usepackage{tgpagella} % text only
 \usepackage{mathpazo}
+
 \usepackage{multicol}
@@
 \setcitestyle{authoryear,open={(},close={)}}
+
+\newcommand{\te}[1]{\text{#1}}
+\newcommand{\mybox}{%
+    \collectbox{%
+        \setlength{\fboxsep}{1pt}%
+        \fbox{\BOXCONTENT}%
+    }%
+}
+\def\C{\mathbb{C}}
+\def\N{\mathbb{N}}
+\def\Q{\mathbb{Q}}
+\def\R{\mathbb{R}}
+\def\Z{\mathbb{Z}}
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
+
+\theoremstyle{plain}% default
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem*{cor}{Corollary}
+\theoremstyle{definition}
+\newtheorem{defn}{Definition}[section]
+\newtheorem{conj}{Conjecture}[section]
+\newtheorem{exmp}{Example}[section]
+\newtheorem{exrc}[exmp]{Exercise}
+\theoremstyle{remark}
+\newtheorem*{comm}{Comment}
+\newtheorem*{note}{Note}
+\newtheorem{caso}{Case}
 
@@
 \section{Evaluation}
+\subsection{Operational Semantics}
+
+\begin{note}
+	The letter $e$ denotes an environment. \\
+	The symbol $\_$ is used whenever a value exists but is content is irrelevant
+	to the semantical rule, or cannot be determined and therefore is discarded.
+\end{note}
+
+\textbf{Dictionaries}
+
+\begin{gather*}
+	\te{Creation} \\
+	\hline \\
+	<\te{e, d}> \Rightarrow \\ \{ (k,v) \in d \mid \forall i,j \in \N \wedge i,j \in \left[1, \abs{d}\right] \land i \neq j \\ \text{such that } k_i \neq k_j \}
+\end{gather*}
+\begin{gather*}
+	\te{Insertion} \\
+	\hline \\
+	\dfrac{ \begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, k} \in \te{ed}> \Rightarrow \te{false} \\
+	\end{aligned} }{<\te{e, insert k v d}> \Rightarrow \te{ed} \cup (\te{k,v})} \\ \\
+	\dfrac{ \begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, k} \in \te{ed}> \Rightarrow \te{true}
+	\end{aligned}}{<\te{e, insert k v d}> \Rightarrow \te{ed} \textbackslash \{(\te{k,\_})\} \cup (k, v) }
+\end{gather*}
+\begin{gather*}
+	\te{Deletion} \\ \hline \\
+	\dfrac{	\begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, k} \in \te{ed}> \Rightarrow \te{true}
+	\end{aligned}}{<\te{e, remove k d}> \Rightarrow \te{ed} \textbackslash \{(\te{k,v})\}} \\ \\
+	\dfrac{	\begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, k} \in \te{ed}> \Rightarrow \te{false}
+	\end{aligned}}{<\te{e, remove k d}> \Rightarrow \te{error}}
+\end{gather*}
+\begin{gather*}
+	\te{Contains key} \\ \hline \\
+	\dfrac{<\te{e, d}> \Rightarrow \te{ed}}{<\te{e}, \te{haskey k d}> \Rightarrow (\te{k, \_}) \in \te{ed}}
+\end{gather*}
+\begin{gather*}
+	\te{Retreive a value} \\ \hline \\
+	\dfrac{	\begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, k} \in \te{ed}> \Rightarrow \te{true}
+	\end{aligned}}{<\te{e, getkey k d}> \Rightarrow \te{v}} \\ \\
+	\dfrac{	\begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, k} \in \te{ed}> \Rightarrow \te{false}
+	\end{aligned}}{<\te{e, getkey k d}> \Rightarrow \te{error}}
+\end{gather*}
+\begin{gather*}
+	\te{Filter by keys} \\ \hline \\
+	\dfrac{	\begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, ks}> \Rightarrow \te{\{k1, ..., kn\}}
+	\end{aligned}}{<\te{e, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{ed} \mid (k \in ks) \}}
+\end{gather*}
+\begin{gather*}
+	\te{Map} \\ \hline \\
+	\dfrac{	\begin{aligned}
+		<\te{e, d}> \Rightarrow \te{ed} \\
+		<\te{e, f}> \Rightarrow \lambda(x)
+	\end{aligned}}
+	{<\te{e, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{ed}  \}}
+\end{gather*}
+\begin{gather*}
+	\te{Fold Left} \\ \hline \\
+	\dfrac{\begin{aligned}
+		<\te{e, f}> \Rightarrow \lambda(x,y)  \\
+		<\te{e, d}> \Rightarrow \{(k_1, v_1), \hdots, (k_n, v_n)\}
+	\end{aligned}}{<\te{e, foldl f a d}> \Rightarrow \lambda( \hdots \lambda(\lambda(a, v_1), v_2), \hdots, v_n)} \\ \\
+\end{gather*}
+
+\section{Javascript Transpiler}
 

### 2020-01-08 paper/paper.tex
rely on ramda.js for javascript transpilation
grammar in paper, added option to exlude js prelude

@@
 %\usepackage{tgpagella} % text only
-\usepackage{mathpazo}
+%\usepackage{mathpazo}
+\usepackage{stix}
 
@@
 \lstdefinestyle{caml} {language=caml, basicstyle=\ttfamily, columns=[c]fixed,
+ keywordstyle=\color{vblue}, identifierstyle=\color{black},
+ commentstyle=\color{vgreen}, upquote=true, commentstyle=, breaklines=true,
+ showstringspaces=false, stringstyle=\color{blue},
+ literate={'"'}{\textquotesingle "\textquotesingle}3}
+
+\lstdefinestyle{txt} {basicstyle=\ttfamily, columns=[c]fixed,
  keywordstyle=\color{vblue}, identifierstyle=\color{black},
@@
 
-\begin{multicols}{2}
-
 \section{Lexer}
@@
 
-\section{Parser}
+\section{Syntax and Parser}
+The parser is realized with the \textbf{Menhir} parser generator, and is
+documented using \textbf{Obelisk}, which generates a clean text file
+containing the grammar documentation
+
+\lstinputlisting[style=txt]{grammar.txt}
+
+\begin{multicols}{2}
 
@@
 simple calculations before writing the program in which they appear in, we rely
-on machines to simplify those processes. Reducing constants before evalaution
+on machines to simplify those processes. Reducing constants before evaluation
 may seem unnecessary when writing a small program, but they do take away
@@
 
+Most of the primitives rely on the Javascript library \textbf{Ramda} \url{https://ramdajs.com/}
+
 \section{Tests}

### 2020-01-15 paper/paper.tex
added bibliography
fixed a bug in including modules from files, working on paper, fixed some docs

@@
-\documentclass[a4paper, 11pt]{article}
+\documentclass[a4paper, 10pt]{article}
 
@@
 %\usepackage{mathpazo}
-\usepackage{stix}
+\usepackage{stix2}
 
@@
 %% Citation package
-\usepackage[authoryear]{natbib}
-\bibliographystyle{abbrvnat}
-\setcitestyle{authoryear,open={(},close={)}}
+%\usepackage[authoryear]{natbib}
+\bibliographystyle{unsrt}
+%\setcitestyle{authoryear,open={(},close={)}}
 
@@
 \begin{abstract}
-\textbf{minicaml} is a small, purely functional interpreted programming language
-with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and Prof.
-Francesca Levi's minicaml, an evaluation example to show students attending the
-Programming 2 course at the University of Pisa how interpreters work. It is an
-interpreted language featuring a Caml-like syntax, static (lexical scoping),
-interchangeable eager and lazy evaluation and a didactical REPL that
-shows each AST expression and each evaluation step.
+\textbf{minicaml} is a dinamically typed and purely functional interpreted
+programming language. It is based on the Professor Gianluigi Ferrari and
+Professor Francesca Levi's minicaml, an evaluation example to show students
+attending the Programming 2 course at the University of Pisa how interpreters
+work. It is an interpreted language heavily inspired from the OCaml, Haskell and
+Scheme languages, with static (lexical scoping), eager and lazy evaluation and a
+didactical REPL that shows each AST expression and each evaluation step.
 \end{abstract}
@@
 Alternatively, \textbf{minicaml} can be installed from source by downloading the
-source code git repository and building it manually. \textbf{minicaml} has been tested
+source code repository and building it manually. \textbf{minicaml} has been tested
 only on Linux and macOS systems. It has not been tested yet on Windows and BSD
@@
 opam install ANSITerminal dune ppx_deriving menhir \\
-  cmdliner alcotest bisect_ppx
+  cmdliner alcotest bisect_ppx ocamline
 # compile
@@
 
-\section{Lexer}
-
-Lexing is achieved with \texttt{ocamllex}, the default tool for generating
-scanners in OCaml
+\begin{multicols}{2}
 
 \section{Syntax and Parser}
+Lexing is achieved with \texttt{ocamllex}, the default tool for generating
+scanners in OCaml.
 The parser is realized with the \textbf{Menhir} parser generator, and is
 documented using \textbf{Obelisk}, which generates a clean text file
-containing the grammar documentation
+containing the language grammar, available in Appendix \ref{grammar}.
 
-\lstinputlisting[style=txt]{grammar.txt}
-
-\begin{multicols}{2}
+\section{Purity Inference}
+An important feature of the minicaml language is the purity inference algorithm,
+which is performed statically on expressions before evaluation. It is an
+interpretation of expressions over the domain of purity, meant to prevent side
+effects by signal an error if they are contained inside the programs written in
+the language. Expressions are tagged by the algorithm with the \texttt{Pure},
+\texttt{Impure} and \texttt{Numerical} labels. An \texttt{Impure} expression is
+an expression that contains calls to primitives that perform I/O operations,
+mutable variables and/or imperative style assignments. A \texttt{Numerical}
+expression is an expression where only numerical operations are performed.
+\texttt{Pure} expressions are those which do not fall into the previous two
+categories. To perform impure side effects, the programmer has two constructs
+available called \textbf{purity blocks}. By default, the evaluator is in an
+\texttt{Uncertain} context, which means that it will not allow side effects to
+be carried on by evaluation, but will allow evaluating purity blocks that change
+the currently allowed purity context. The \texttt{impure} statement takes an
+expression (the block) and evaluates it in a context where the allowed purity is
+\texttt{Impure}, so that side effects may be performed. The other construct
+available, the \texttt{pure} statement, takes an expression and enforces a
+\texttt{Pure} context, meaning that side effects and nested impure blocks will
+not be allowed inside of the expression.
 
 \section{AST Optimization}
-Before being evaluated, AST expressions are analyzed and optimized by an
+After purity inference is performed, and before evaluation, AST expressions are analyzed and optimized by an
 optimizer function that is recursively called over the tree that is representing
@@
 \section{Evaluation}
+\texttt{minicaml}'s evaluator is heavily inspired by the Metacircular Evaluator defined in the highly acclaimed textbook \textit{Structure and Interpretation of Computer Programs} \cite{Abelson1996}
 \subsection{Operational Semantics}
@@
 
-\section{Javascript Transpiler}
-
-Most of the primitives rely on the Javascript library \textbf{Ramda} \url{https://ramdajs.com/}
-
 \section{Tests}
@@
 \begin{itemize}
-	\item Prof. Gian-Luigi Ferrari for teaching us how to project and develop
+	\item Prof. Gian-Luigi Ferrari and Francesca Levi for teaching us how to project and develop
 	interpreters in OCaml
@@
 	\item Prof. Alessandro Berarducci for helping me study lambda calculus in deep.
+	\item Giorgio Mossa for helping me polish the lambda-closure mechanism.
 \end{itemize}
@@
 \end{multicols}
+
+\appendix
+\clearpage
+\section{Parsing Grammar}
+\label{grammar}
+
+\lstinputlisting[style=txt]{grammar.txt}
+
+\bibliography{bib}
+
 \end{document}

### 2020-01-16 paper/paper.tex
mutable states in file runner

@@
 \usepackage{amsthm}
+\usepackage[title]{appendix}
 \usepackage{collectbox}
@@
 %% Sets page size and margins. You can edit this to your liking
-\usepackage[top=1.3cm, bottom=2.0cm, outer=2.5cm, inner=2.5cm, heightrounded,
-marginparwidth=1cm, marginparsep=0.4cm, margin=1.2cm]{geometry}
+\usepackage[top=1.3cm, bottom=2.0cm, outer=1.2cm, inner=1.2cm, heightrounded,
+marginparwidth=1cm, marginparsep=0.4cm]{geometry}
 
@@
  commentstyle=\color{vgreen}, upquote=true, commentstyle=, breaklines=true,
- showstringspaces=false, stringstyle=\color{blue},
+ showstringspaces=false, stringstyle=\color{blue}, tabsize=2,
  literate={'"'}{\textquotesingle "\textquotesingle}3}
@@
 \begin{abstract}
-\textbf{minicaml} is a dinamically typed and purely functional interpreted
+\textbf{minicaml} is a dyhamically typed and purely functional interpreted
 programming language. It is based on the Professor Gianluigi Ferrari and
@@
 An important feature of the minicaml language is the purity inference algorithm,
-which is performed statically on expressions before evaluation. It is an
-interpretation of expressions over the domain of purity, meant to prevent side
-effects by signal an error if they are contained inside the programs written in
-the language. Expressions are tagged by the algorithm with the \texttt{Pure},
-\texttt{Impure} and \texttt{Numerical} labels. An \texttt{Impure} expression is
-an expression that contains calls to primitives that perform I/O operations,
-mutable variables and/or imperative style assignments. A \texttt{Numerical}
-expression is an expression where only numerical operations are performed.
-\texttt{Pure} expressions are those which do not fall into the previous two
-categories. To perform impure side effects, the programmer has two constructs
+which is performed statically on expressions before evaluation. It is an interpretation of expressions over the domain of purity, meant to
+prevent side effects by signal an error if they are contained inside the
+programs written in the language. Expressions are tagged by the algorithm with
+the \texttt{Pure}, \texttt{Impure} and \texttt{Numerical} labels. An
+\texttt{Impure} expression is an expression that contains calls to primitives
+that perform I/O operations, mutable variables and/or imperative style
+assignments. A \texttt{Numerical} expression is an expression where only
+numerical operations are performed; \texttt{Pure} expressions are those which do not fall into the previous two
+categories.
+
+To achieve the execution of impure side effects, the programmer has two constructs
 available called \textbf{purity blocks}. By default, the evaluator is in an
@@
 
-\section{Evaluation}
-\texttt{minicaml}'s evaluator is heavily inspired by the Metacircular Evaluator defined in the highly acclaimed textbook \textit{Structure and Interpretation of Computer Programs} \cite{Abelson1996}
+\section{Evaluator}
+\texttt{minicaml}'s evaluator is heavily inspired by the Metacircular Evaluator defined in the
+highly acclaimed textbook \textit{Structure and Interpretation of Computer Programs} \cite{Abelson1996}.
+
+\section{Primitives}
+The language primitives that are implemented in OCaml are organized in modules
+separated by functionality. Each primitive is a function that accepts a list of
+evaluated values and returns a single reduced value; therefore they have a type
+of \texttt{evt list -> evt}. OCaml primitives have to perform internal
+typechecking and unpacking of the arguments they receive from the minicaml
+calls.
+
+From the evaluator's perspective, primitives are organized in a table
+such that when a symbol gets evaluated, it is looked up in the primitives table,
+if there is a match then the found primitive's name is wrapped in an
+\texttt{ApplyPrimitive} expression nestedinside of a lazy lambda expression that
+permits partial application. When the evaluator finally encounters an
+\texttt{ApplyPrimitive} expression, the primitive OCaml function is extracted,
+applied to the arguments and the resulting value is returned by the current
+evaluator call. If a primitive is not found when looking up for a symbol, then a
+symbol lookup is performed in the current environment.
+
+Some primitives, such as catamorphic procedures, are not native OCaml functions
+but small expressions written directly in minicaml; those primitives are kept as
+lazy expressions into the same table as native OCaml primitives. The key
+difference between the two resides in the fact that those textual minicaml
+primitives are not transformed into a function which body contains only an
+\texttt{ApplyPrimitive} call, but are instead parsed and analyzed at run time.
+The resulting additional startup time caused by parsing and analysis is
+proportional to the number of textual form primitives in the table and therefore
+quite irrelevant on non-embedded computer systems. The \textit{fold left} and
+\textit{fold right} catamorphic primitives are written directly in the minicaml
+language and are hereby provided as examples.
+
+\begin{lstlisting}[style=caml,caption=The tail recursive left fold procedure]
+fun f z l ->
+if typeof l = "list" then
+  let aux = fun f z l ->
+    if l = [] then z else
+	  aux f (f z (head l)) (tail l)
+	in aux f z l
+else if typeof l = "dict" then
+	let aux = fun f z kl vl ->
+		if kl = [] && vl = [] then z else
+		aux f (f z (head vl)) (tail kl) (tail vl)
+	in aux f z (getkeys l) (getvalues l)
+else failwith "value is not iterable"
+\end{lstlisting}
+
+\begin{lstlisting}[style=caml,caption=The right fold procedure]
+fun f z l ->
+if typeof l = "list" then
+   let aux = fun f z l ->
+	  if l = [] then z else
+	  f (head l) (aux f z (tail l))
+   in aux f z l
+else if typeof l = "dict" then
+   let aux = fun f z kl vl ->
+	  if kl = [] && vl = [] then z else
+	  f (head vl) (aux f z (tail kl) (tail vl))
+   in aux f z (getkeys l) (getvalues l)
+else failwith "value is not iterable"
+\end{lstlisting}
+
+\section{Tests}
+Unit testing is extensively performed using the alcotest testing framework. Code
+coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
+page containing the coverage percentage when unit tests are run by the dune
+build system. After each commit is pushed to the remote version control repository on
+Github, the package is built and tests are run thanks to the Travis Continuos
+Integration system.
+
+\section{Thanks to}
+
+\begin{itemize}
+	\item Prof. Gian-Luigi Ferrari and Francesca Levi for teaching us how to project and develop
+	interpreters in OCaml
+	\item Antonio DeLucreziis for helping me implement lazy evaluation.
+	\item Prof. Alessandro Berarducci for helping me study lambda calculus in deep.
+	\item Giorgio Mossa for helping me polish the lambda-closure mechanism.
+\end{itemize}
+
+\end{multicols}
+
+\iffalse
 \subsection{Operational Semantics}
@@
 
-\section{Tests}
-Unit testing is extensively performed using the alcotest testing framework. Code
-coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
-page containing the coverage percentage when unit tests are run by the dune
-build system. After each commit is pushed to the remote version control repository on
-Github, the package is built and tests are run thanks to the Travis Continuos
-Integration system.
+\fi
 
-\section{Thanks to}
+\clearpage
 
-\begin{itemize}
-	\item Prof. Gian-Luigi Ferrari and Francesca Levi for teaching us how to project and develop
-	interpreters in OCaml
-	\item Antonio DeLucreziis for helping me implement lazy evaluation.
-	\item Prof. Alessandro Berarducci for helping me study lambda calculus in deep.
-	\item Giorgio Mossa for helping me polish the lambda-closure mechanism.
-\end{itemize}
-
-\end{multicols}
-
-\appendix
-\clearpage
+\begin{appendices}
   \section{Parsing Grammar}
   \label{grammar}
-
   \lstinputlisting[style=txt]{grammar.txt}
+\end{appendices}
 

### 2020-01-17 paper/paper.tex
fixed typo
renamed project

@@
 
-\title{Minicaml, a purely functional, didactical programming language\\WORK IN PROGRESS DRAFT}
+\title{Gobba, a purely functional, didactical programming language\\WORK IN PROGRESS DRAFT}
 \author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
@@
 \begin{abstract}
-\textbf{minicaml} is a dyhamically typed and purely functional interpreted
+\textbf{gobba} is a dynamically typed and purely functional interpreted
 programming language. It is based on the Professor Gianluigi Ferrari and
@@
 \subsection{Installation}
-\textbf{minicaml} is available in the opam 2.0 repository.
-(\url{https://opam.ocaml.org/}). The easiest way to install minicaml is with the
+\textbf{gobba} is available in the opam 2.0 repository.
+(\url{https://opam.ocaml.org/}). The easiest way to install gobba is with the
 OCaml package manager \textbf{opam}. To do so, please check that you have a version of opam $\geq$
@@
 \begin{lstlisting}[style=bash]
-opam install minicaml
+opam install gobba
 \end{lstlisting}
-Alternatively, \textbf{minicaml} can be installed from source by downloading the
-source code repository and building it manually. \textbf{minicaml} has been tested
+Alternatively, \textbf{gobba} can be installed from source by downloading the
+source code repository and building it manually. \textbf{gobba} has been tested
 only on Linux and macOS systems. It has not been tested yet on Windows and BSD
@@
 # download the source code
-git clone https://github.com/0x0f0f0f/minicaml
+git clone https://github.com/0x0f0f0f/gobba
 # cd into the source code directory
-cd minicaml
+cd gobba
 # install dependencies
@@
 \section{Purity Inference}
-An important feature of the minicaml language is the purity inference algorithm,
+An important feature of the gobba language is the purity inference algorithm,
 which is performed statically on expressions before evaluation. It is an interpretation of expressions over the domain of purity, meant to
@@
 \section{Evaluator}
-\texttt{minicaml}'s evaluator is heavily inspired by the Metacircular Evaluator defined in the
+\texttt{gobba}'s evaluator is heavily inspired by the Metacircular Evaluator defined in the
 highly acclaimed textbook \textit{Structure and Interpretation of Computer Programs} \cite{Abelson1996}.
@@
 of \texttt{evt list -> evt}. OCaml primitives have to perform internal
-typechecking and unpacking of the arguments they receive from the minicaml
+typechecking and unpacking of the arguments they receive from the gobba
 calls.
@@
 Some primitives, such as catamorphic procedures, are not native OCaml functions
-but small expressions written directly in minicaml; those primitives are kept as
+but small expressions written directly in gobba; those primitives are kept as
 lazy expressions into the same table as native OCaml primitives. The key
-difference between the two resides in the fact that those textual minicaml
+difference between the two resides in the fact that those textual gobba
 primitives are not transformed into a function which body contains only an
@@
 quite irrelevant on non-embedded computer systems. The \textit{fold left} and
-\textit{fold right} catamorphic primitives are written directly in the minicaml
+\textit{fold right} catamorphic primitives are written directly in the gobba
 language and are hereby provided as examples.

### 2020-01-18 paper/paper.tex
renamed project in paper
separated list and dictionary iterator primitives in their appropriate modules

@@
 \usepackage{xcolor}
+\usepackage{caption}
 \usepackage{mathtools}
@@
 
-\title{Gobba, a purely functional, didactical programming language\\WORK IN PROGRESS DRAFT}
+\title{The gobba functional programming language.\\WORK IN PROGRESS DRAFT}
 \author{Alessandro Cheli\\Course taught by Prof. Gianluigi Ferrari\\and Prof. Francesca Levi}
@@
 \maketitle
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.15\textwidth]{../assets/gobba.png}
+	\captionsetup{labelformat=empty}
+	\caption{The gobba logo by Kevin Fontanari}
+\end{figure}
 
@@
 work. It is an interpreted language heavily inspired from the OCaml, Haskell and
-Scheme languages, with static (lexical scoping), eager and lazy evaluation and a
-didactical REPL that shows each AST expression and each evaluation step.
+Scheme languages, with static (lexical scoping), a simple but effective module
+system, eager and lazy evaluation and a didactical REPL that shows each AST
+expression and each evaluation step.
 \end{abstract}
@@
 \subsection{Installation}
-\textbf{gobba} is available in the opam 2.0 repository.
-(\url{https://opam.ocaml.org/}). The easiest way to install gobba is with the
-OCaml package manager \textbf{opam}. To do so, please check that you have a version of opam $\geq$
+
+The easiest way to install gobba is with the
+OCaml package manager \textbf{opam} (\url{https://opam.ocaml.org/}).
+gobba is available in the opam 2.0 repository; to install the language from opam, please check that you have a version of opam $\geq$
 2.0.0 and run:
@@
 make
-# test
-make test
-# execute
-make run
-# install
-make install
+# test, execute and install
+make test; make run; make install
 \end{lstlisting}
@@
 	interpreters in OCaml
+	\item Kevin Fontanari for the pixel art gobba mascotte.
 	\item Antonio DeLucreziis for helping me implement lazy evaluation.

### 2020-01-19 paper/paper.tex
added completion with the latest ocamline library and ocaml-linenoise. quite broken

@@
 \textbf{gobba} is a dynamically typed and purely functional interpreted
-programming language. It is based on the Professor Gianluigi Ferrari and
-Professor Francesca Levi's minicaml, an evaluation example to show students
-attending the Programming 2 course at the University of Pisa how interpreters
-work. It is an interpreted language heavily inspired from the OCaml, Haskell and
-Scheme languages, with static (lexical scoping), a simple but effective module
-system, eager and lazy evaluation and a didactical REPL that shows each AST
+programming language. Based on Professors Gianluigi Ferrari and Francesca Levi's
+minicaml interpreter example, the goal for gobba is to be a practical language with
+built in support for scientific computing, solving some of the problems that
+exist in other dynamically typed interpreted languages like python and Javascript. It is an
+interpreted language heavily inspired from the OCaml, Haskell and Scheme
+languages, with static (lexical scoping), a simple but effective module system,
+eager and lazy evaluation and a didactical REPL that can show each AST
 expression and each evaluation step.
@@
 
-\section{REPL and command line interface}
-\subsection{Installation}
+\section{Installing gobba}
 
@@
 \begin{multicols}{2}
+
+\section{Interactive Command Line Interface}
+If no filename is passed to \texttt{gobba} executable, the interactive shell
+interface is launched. The REPL shell is built upon a simple library called
+\texttt{ocamline} \cite{ocamline}, which itself relies on a library called
+\texttt{ocaml-linenoise} \cite{linenoise} that provides \texttt{readline}
+navigation and completion functionality without additional system
+dependencies.
 

### 2020-01-19 paper/paper.tex
paper and readme

@@
 \usepackage[title]{appendix}
+\usepackage[nottoc]{tocbibind}
 \usepackage{collectbox}
@@
 \usepackage{graphicx} %allows you to use jpg or png images. PDF is still recommended
-\usepackage[colorlinks=False]{hyperref} % add links inside PDF files
+\usepackage[hidelinks]{hyperref} % add links inside PDF files
 \usepackage{amsmath}  % Math fonts
@@
 %% Citation package
-%\usepackage[authoryear]{natbib}
-\bibliographystyle{unsrt}
+\usepackage[square,numbers]{natbib}
+\bibliographystyle{abbrvnat}
 %\setcitestyle{authoryear,open={(},close={)}}
@@
 \textbf{gobba} is a dynamically typed and purely functional interpreted
-programming language. Based on Professors Gianluigi Ferrari and Francesca Levi's
-minicaml interpreter example, the goal for gobba is to be a practical language with
-built in support for scientific computing, solving some of the problems that
-exist in other dynamically typed interpreted languages like python and Javascript. It is an
-interpreted language heavily inspired from the OCaml, Haskell and Scheme
-languages, with static (lexical scoping), a simple but effective module system,
-eager and lazy evaluation and a didactical REPL that can show each AST
-expression and each evaluation step.
+programming language, heavily inspired from the OCaml,
+Haskell and Scheme languages. It is based on Professors Gianluigi Ferrari and Francesca Levi's
+minicaml interpreter example. The goal for gobba is to be a practical language
+with built in support for scientific computing, solving some of the problems
+that exist in other dynamically typed interpreted languages like python and
+Javascript. It features static (lexical scoping), a simple but
+effective module system, eager and lazy evaluation and an interactive didactical
+REPL that shows completions and can show insights about each recursive evaluation step.
 \end{abstract}
@@
 Lexing is achieved with \texttt{ocamllex}, the default tool for generating
-scanners in OCaml.
-The parser is realized with the \textbf{Menhir} parser generator, and is
-documented using \textbf{Obelisk}, which generates a clean text file
-containing the language grammar, available in Appendix \ref{grammar}.
+scanners in OCaml. The parser is realized with the \textbf{Menhir} parser
+generator library \cite{menhir}, and is documented using \textbf{Obelisk}, which
+generates a clean text file containing the language grammar, available in
+Appendix \ref{grammar}.
 
